Weak lensing Hierarchy Bayesian Inference

### 2013-02-13 write-up.tex
update write-up.tex

\date{03/09/2013}
\maketitle
\begin{abstract}
We present a Hierarchy Bayesian method for shear inference in Weak
Lensing survey. With this method we are able to infer synchronously
cosmic shear at different sky patches as well as the intrinsic shape
distribution. We show that this Hierarchy Bayesian method is more
accurate than the traditional average method and (prove to a large
extent )it is an unbiased estimation of shear.

@@

The measurement of cosmic shear is determined by the amount of distortion
caused to a forewground galaxy. Due to the isotropic universe the
expect value of a galaxy's intrinsic complex ellipticity is 0. Therefore
the comples ellipticity of a stretched galaxies is an unbiased estimation
of cosmic shear(Bartelmann \& Schneider 2001).However, the distortion
induced by cosmic shear is typically on the order of a few percent,which
is significantly smaller than the galaxies's intrinsic shape noise(\textasciitilde{}0.1
level).

@@

While in this paper what we want to focus is how to use a beysian
approach to infere cosmic shear independent from which way the galaxy
shape is measured with better accuracy than traditional averaging
method.Therefore in the toy model we used,we assume we have perfect
measurement on the galaxy shape.

One of the major problems for a bayesian inference of shear is that
even though a lot of measurement have bean made ,we still know little
about the intrinsic ellipticity distribution of galaxies of the whole
universe(Leauthaud\&Massey 2007;Joachimi\&Semboloni2012).However in
our Hierarchy Bayesian method we avoid to making any assumption on
intrinsic ellipticity distribution.We will show that using a free
model for intrinsic ellipticity distribution and infere its parameters
together with cosmic shear we will still out perform the traditional
averaging method.

>>>>

\date{02/13/2013}
\maketitle
\begin{abstract}
We present a Hierarchy Bayesian method for shear inference in Weak
Lensing survey. With this method we are able to infer synchronously
cosmic shear at different sky patches as well as the intrinsic shape
distribution. We show that this Hierarchy Bayesian method is more
accurate than the traditional average method and (prove to a large
extent )it is an unbiased estimation of shear.

@@

The measurement of cosmic shear is determined by the amount of distortion
caused to a foreground galaxy. Due to the isotropy of the Universe
the expect value of a galaxy's intrinsic complex ellipticity $\epsilon$
is 0. Therefore the comples ellipticity of a stretched galaxies is
an unbiased estimation of cosmic shear(Bartelmann \& Schneider 2001).However,
the distortion induced by cosmic shear is typically on the order of
a few percent,which is significantly smaller than the galaxies's intrinsic
shape noise(\textasciitilde{}0.1 level).

@@

While in this paper what we want to focus is how a hierarchy beysian
approach can infer cosmic shear independently from which way the galaxy
shape is measured with better accuracy than traditional averaging
method.Therefore in the toy model we used,we assume we have perfect
measurement on the galaxy shape.

One of the major problems of a bayesian inference of cosmic shear
is that even though a lot of measurement have bean made ,we still
know little about the intrinsic ellipticity distribution of galaxies
of the whole universe(Leauthaud\&Massey 2007;Joachimi\&Semboloni2012).However
in our Hierarchy Bayesian method we avoid to making up any empirical
model for intrinsic ellipticity distribution.We will show that using
a free form model for intrinsic ellipticity distribution and infer
its parameters together with cosmic shear we can still out perform
the traditional averaging method.
